Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-07-01 sattose/paper.tex
Stuff

\subsection{Research questions}
We have formalized the following research questions in order to improve upon the state-of-the-art in code duplication refactoring:\\
\textbf{RQ1.} How can we define clone types such that they \textbf{can} be automatically refactored?\\
%\textbf{RQ2.} How can we determine decision factors for when a clone \textbf{should} be refactored?\\
\textbf{RQ2.} What are the discriminating factors to decide when a clone \textbf{should} be refactored?\\
\textbf{RQ3.} To what extent can we \textbf{automate} the process of refactoring clones?\\

@@

\subsection{Clone types}\label{chap:backgroundclonetypes}
In a 2007 survey by Roy et al.~\cite{roy2007survey} he defines several types of clones:\\
\textbf{Type 1:} Identical code fragments except for variations in whitespace (may also be variations in layout) and comments.\\
\textbf{Type 2:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
\textbf{Type 3:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.\\

@@

We also measured the duration of finding clones by the different clone types. These results are displayed in figure TODO.

@@

\subsection{Relations Between Clone Instances} \label{chap:relationsinstances}
When merging code clones in object-oriented languages, it is very important to consider the relation between clone instances. This relation has a big impact on how a clone should be refactored, in order to improve the software design in the process. In this section, we display measurements we conducted on the corpus introduced in Sec.~\ref{chap:corpus}. These measurements are based on an experiment by Fontana et al.~\cite{fontana2015duplicated}, which we will briefly introduce in Sec.~\ref{chap:catcloneinstancerelations}. We use a vastly different setup, which is explained in Sec.~\ref{chap:oursetup}. We then show our results in Sec.~\ref{chap:ourmeasurements}.

@@

\subsubsection{Our setup}\label{chap:oursetup}
We use a similar setup to that used by Fontana et al. (Table~3 of Fontana et al.~\cite{fontana2015duplicated}). Fontana et al. measure clones using their own tool (DCRA). As explained in section~\ref{ch:tool-overview}, we chose to implement our own tool, CloneRefactor. Therefore, the setup for our measurements differs as follows from Fontana et al.:
\begin{itemize}
  \item We consider clone classes rather than clone pairs. The rationale for this is given in Sec.~\ref{chap:cloneclasses}.
\item We use different thresholds regarding when a clone should be considered. Fontana et al. seek clones that span a minimum of 7 source lines of code (SLOC). We seek clones with a minimum size of 6 statements/declarations. This is explained detail in Sec.~\ref{chap:thresholds}.
\item We seek duplicates by statement/declaration rather than SLOC. This makes our analysis depend less on the coding style (in terms of newline usage) of the author of the software project.
\item We test a broader range of projects. Fontana et al. use a set of 50 relatively large projects. We use the corpus as explained in \ref{chap:corpus}, which contains a diverse set of projects (diverse both in volume and code quality).
\end{itemize}

\subsubsection{Our results} \label{chap:ourmeasurements}
Table~\ref{table:relations} contains our results regarding the relations between clone instances. In this table, ``T1'' stands for the type 1 algorithm from literature and ``1R'' stands for our T1R definition as explained in Sec.~\ref{sec:type1r}.

\begin{table}[H]
  \begin{center}
  \caption{Clone relations} \label{table:relations}
  \medskip
\begin{tabular}{|l|l|l|l|l|} \hline
\textbf{Relation}  & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
Unrelated          & 6,134           & 35.48  & 4,762 & 38.14            \\ \hline
\begin{tabular}[c]{@{}l@{}}Same\\Class\end{tabular}          & 4,772            & 27.60  & 3,131 & 25.07             \\ \hline
Sibling            & 2,680            & 15.50   & 1,949 & 15.61            \\ \hline
\begin{tabular}[c]{@{}l@{}}Same\\Method\end{tabular}         & 2,247            & 13.00   & 1,685 & 13.49             \\ \hline
\begin{tabular}[c]{@{}l@{}}External\\Superclass\end{tabular} & 794            & 4.59   & 558 & 4.47             \\ \hline
\begin{tabular}[c]{@{}l@{}}First\\Cousin\end{tabular}        & 269             & 1.56     & 197 & 1.58           \\ \hline
Superclass         & 237             & 1.37     & 118 & 0.94           \\ \hline
\begin{tabular}[c]{@{}l@{}}Common\\Hierarchy\end{tabular}    & 123             & 0.71    & 73 & 0.58            \\ \hline
Ancestor           & 35              & 0.20     & 14 & 0.11          \\ \hline
\end{tabular}
\end{center}
\end{table}

>>>>

\subsection{Research questions}
We have formalized the following research questions in order to improve upon the state-of-the-art in code duplication refactoring:
\\\\
\textbf{RQ1.} How can we define clone types such that they \textbf{can} be automatically refactored?\\
%\textbf{RQ2.} How can we determine decision factors for when a clone \textbf{should} be refactored?\\
\textbf{RQ2.} What are the discriminating factors to decide when a clone \textbf{should} be refactored?\\
\textbf{RQ3.} To what extent can we \textbf{automate} the process of refactoring clones?\\

@@

\subsection{Clone types}\label{chap:backgroundclonetypes}
In a 2007 survey by Roy et al.~\cite{roy2007survey} he defines several types of clones:
\\\\
\textbf{Type 1:} Identical code fragments except for variations in whitespace (may also be variations in layout) and comments.\\
\textbf{Type 2:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
\textbf{Type 3:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.\\

@@

We also measured the duration of finding clones by the different clone types. These results are displayed in figure \ref{fig:performance}. Although this data is dependent on the implementation, there is a notable difference between the refactoring-oriented clone types and the literature clone types. Most of the time that the refactoring-oriented clone types take longer is spent resolving symbols (to infer FQIs).

\begin{figure}[H]
  \caption{Duration in minutes of identifying clones for clone type definitions.}
    \includegraphics[width=1\columnwidth]{img/TypeResults}
  \label{fig:performance}
\end{figure}

@@

All data shown in this section is measured using the T1R clone definition. We have performed the same measurements for the other type definitions and found that they follow similar trends. Because of that, we decided not to further show them in this section.

\subsection{Relations Between Clone Instances} \label{chap:relationsinstances}
When merging code clones in object-oriented languages, it is very important to consider the inheritance relation between clone instances. This relation has a big impact on how a clone should be refactored.

@@

We use a similar setup to that used by Fontana et al. (Table~3 of Fontana et al.~\cite{fontana2015duplicated}). Fontana et al. measure clones using their own tool (DCRA). As explained in section~\ref{ch:tool-overview}, we chose to implement our own tool, CloneRefactor. Therefore, the setup for our measurements differs as follows from Fontana et al.:
\begin{itemize}
  \item We consider clone classes rather than clone pairs. The rationale for this is given in Sec.~\ref{chap:cloneclasses}.
\item We use different thresholds regarding when a clone should be considered. Fontana et al. seek clones that span a minimum of 7 source lines of code (SLOC). We seek clones with a minimum size of 6 statements/declarations. This is explained detail in Sec.~\ref{chap:thresholds}.
\item We seek duplicates by statement/declaration rather than SLOC. This makes our analysis depend less on the coding style (in terms of newline usage) of the author of the software project.
\item We test a broader range of projects. Fontana et al. use a set of 50 relatively large projects. We use the corpus as explained in \ref{chap:corpus}, which contains a diverse set of projects (diverse both in volume and code quality).
\end{itemize}

Table~\ref{table:relations} contains our results regarding the relations between clone instances.

\begin{table}[H]
  \begin{center}
  \caption{Clone relations} \label{table:relations}
  \medskip
\begin{tabular}{|l|l|l|} \hline
\textbf{Relation} & \textbf{\#} & \textbf{\%} \\ \hline
Unrelated          & 4,762 & 38.14            \\ \hline
Same Class          & 3,131 & 25.07             \\ \hline
Sibling               & 1,949 & 15.61            \\ \hline
Same Method         & 1,685 & 13.49             \\ \hline
External Superclass   & 558 & 4.47             \\ \hline
First Cousin          & 197 & 1.58           \\ \hline
Superclass          & 118 & 0.94           \\ \hline
Common Hierarchy    & 73 & 0.58            \\ \hline
Ancestor          & 14 & 0.11          \\ \hline
\end{tabular}
\end{center}
\end{table}
